A comprehensive study of the early phylodynamics of SARS-CoV-2 in Europe

### 2020-11-27 reports/paper/main.tex
wip results paper

@@

In Figure \ref{fig:first_src}, we are looking at the ordered set of introduction intoo european countries. For each trajectory, we have the fist introduction into each country happening in a determined order, i.e. the first european country with a covid case, the second country with a covid case... So we are vissualizing the number of trajectories that share the same order of first cases. More trajectories where the first case was to Germany, no clear order after the first country. Spain last one.\\
\todo{Explain this better}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\textwidth]{201014_europe2_figtraj02.png}
    \caption{Inferred population size trajectories over time. A subsampled set of 200 inferred trajectories is plotted. In each subplot, the trajectories (solid lines) are compared with the ECDC total case count data (dashed line).}
    \label{fig:trajs}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{201014_europe2_figtraj04.png}
    \caption{}
    \label{fig:first_dest}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{201014_europe2_figtraj05.png}
    \caption{}
    \label{fig:first_src}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\textwidth]{201014_europe2_figtraj02.png}
    \caption{Inferred population size trajectories over time. A subsampled set of 200 inferred trajectories is plotted. In each subplot, the trajectories (solid lines) are compared with the ECDC total case count data (dashed line).}
    \label{fig:trajs}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{201014_europe2_figtraj04.png}
    \caption{Ordered set of countries by its first introduction, i.e. first case in the country. The color corresponds to the first country with a case, and the size of the box with the country name / ribbon / flux is the number / proportion of trajectories that have that particular order of first introductions.} 
    \label{fig:first_dest}
\end{figure}

In Figure \ref{fig:first_src}, we are looking at the ordered set of introduction intoo european countries. For each trajectory, we have the fist introduction into each country happening in a determined order, i.e. the first european country with a covid case, the second country with a covid case... So we are vissualizing the number of trajectories that share the same order of first cases. More trajectories where the first case was to Germany, no clear order after the first country. Spain and Other European last one.\\
\todo{Explain this better}

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{201014_europe2_figtraj05.png}
    \caption{Ordered set of countries by its first migration, i.e. spreading event out of the country. The color corresponds to the last country with a migration to other countries. The size of the box with the country name / ribbon / flux is the number / proportion of trajectories that have that particular order of first migrations.}
    \label{fig:first_src}
\end{figure}

@@
